Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys

### 2023-11-14 SEIR.tex
address comments

Mechanistic models explicitly represent the infection process driving the spread of infectious disease.
Infectious diseases have inherent feedback loops: current infectious individuals generate future infectious individuals.
Explicitly representing this system can generate insights not possible with the statistical methods used in the previous chapter.

@@

This section gradually builds complexity into a mechanistic model.
The class of mechanistic models considered here is \emph{compartmental} models, the most common type of mechanistic infectious disease model.
A compartmental model divides all members of the population under study into compartments, each representing a disease state.
They can be \emph{deterministic} or \emph{stochastic}.

>>>>

Mechanistic models explicitly represent the infection process driving the spread of infectious disease.
Infectious diseases have inherent feedback loops: current infectious individuals generate future infectious individuals.
Explicitly representing this system can generate insights not possible with the statistical methods used in the previous chapter\todo{give explicit examples of advantages}.

@@

\todo[inline]{integrate this paragraph into the intro part}
This section gradually builds complexity into a mechanistic model.
The class of mechanistic models considered here is \emph{compartmental} models, the most common type of mechanistic infectious disease model.
A compartmental model divides all members of the population under study into compartments, each representing a disease state.
They can be \emph{deterministic} or \emph{stochastic}.
